Optimal (Multiway) Spatial Joins

### 2024-05-27 msj.tex
yufei

As mentioned before, for a result tuple $(r_1, ..., r_{k-2}, h, v)$ of this type, a rectangle $r_i$, for some $i \in [k-2]$, covers an endpoint of $h$ or $v$ or both. As (i) there are $k-2$ choices for $i$ and (ii) $h$ and $v$ together have four endpoints, we can divide Type 2 further into $4(k-2)$ ``sub-types'': in subtype 1 (resp., 2), $r_1$ covers the left (resp., right) endpoint of $h$, in subtype 3 (resp., 4), $r_1$ covers the bottom (resp., top) endpoint of $v$, in subtype 5 (resp., 6), $r_2$ covers the left (resp., right) endpoint of $h$, etc. It is possible for the result tuple to belong to multiple sub-types simultaneously.

Next, we will focus on producing the result tuples of a particular sub-type: those tuples $(r_1, ..., r_{k-2}, h, v)$ where $r_{k-2}$ covers the left endpoint of $h$ --- let us denote this set of result tuples as $\J_2$. Other sub-types can be computed using the same algorithm, by symmetry.

>>>>

As mentioned before, for a result tuple $(r_1, ..., r_{k-2}, h, v)$ of this type, a rectangle $r_i$, for some $i \in [k-2]$, covers an endpoint of $h$ or $v$ or both. As (i) there are $k-2$ choices for $i$ and (ii) $h$ and $v$ together have four endpoints, we can divide Type 2 further into $4(k-2)$ ``sub-types'': in subtype 1 (resp., 2), $r_1$ covers the left (resp., right) endpoint of $h$, in subtype 3 (resp., 4), $r_1$ covers the bottom (resp., top) endpoint of $v$, in subtype 5 (resp., 6), $r_2$ covers the left (resp., right) endpoint of $h$, etc. It is possible for the result tuple to belong to multiple sub-types simultaneously. Next, we will focus on producing the result tuples of a particular sub-type:
\myeqn{
    \J_2  &=& \{(r_1, ..., r_{k-2}, h, v) \in \J(R1, ..., R_{k-2}, H, V) \mid \text{$r_{k-2}$ covers} \nn \\[-1mm]
    && \text{the left endpoint of $h$}\}. \nn
}
Other sub-types can be found analogously.
